Price of Anarchy for Mean Field Games

### 2018-07-24 PoA.tex
update again prop 4 finish
stylistic edits

We study in the following the variation of $PoA$ by letting one of the coefficients tend to zero or to infinity. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right), & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1), & \qquad & 
		A^\eta &=& - b_1, \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}}, \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s)),& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2, & \qquad &
		C^\eta &=& q + \bar{q}, \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)), & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2, & \qquad & 
		D^\eta &=& q_T + \bar{q}_T .
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}},
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. Note that under the above conditions, we have $\delta^-_u<0<\delta^+_u$ and thus, $u_t \geq 0$ for all $t\in[0,T]$. We have analogous expressions for $w_t$ and $\eta_t$, which are also nonnegative, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$, and the above conditions on the parameters $B$, $C^u$, $D^u$, $C^w$, $D^w$, $B^\eta$, $C^\eta$, and $D^\eta$ are exactly the conditions in assumption (\ref{eq:assumptions}).

@@

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\left\vert u_t^{r} \right\vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	% lower bound for (b_2 + b2 bar) u_t
	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}). Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$, for example $\epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$. Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert  \right\} \leq \epsilon_1,
	$$ 
	so that
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}

@@

%	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	We first provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. Let $\epsilon_1 > 0$ satisfy $\epsilon_1 < \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$, there exists $\bar{b}_2^{*,u} := \bar{b}^{*,u}_2(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert \right\} \leq \epsilon_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$:
	\begin{IEEEeqnarray*}{rCl}
		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + \left( - \delta_u^{-,\bar{b}_2} + \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) } \\
		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
		&\leq & \frac{\epsilon_1 + \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_u(\epsilon_1)
	\end{IEEEeqnarray*}
	Idem, we can also have a uniform bound for $w_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. There exists $\bar{b}_2^{*,w} := \bar{b}_2^{*,w}(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,w}$ we have:
	\begin{equation*}
		\vert w_t^{\bar{b}_2} \vert \leq \frac{\epsilon_1 + D^w (2 c_{\delta_w^{\bar{b}_2\to \infty}} + 2 \epsilon_1)}{c_{\delta_w^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_w(\epsilon_1).		
	\end{equation*}
	Let $\bar{b}^{*,upper}_2 = \max\{ \bar{b}_2^{*,u}, \bar{b}_2^{*,w} \}$ and $M(\epsilon_1) = \max\{ M_u(\epsilon_1), M_v(\epsilon_1) \}$, then we have
	\begin{equation}
	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
	\end{equation}

@@

\subsection*{\textbf{Scalar Riccati Equation}} If the scalar Riccati equation 
	\begin{equation*}
		\dot{\rho}_t - B \rho_t^2 - 2A \rho_t  + C = 0 
	\end{equation*}
	with terminal condition $\rho_T = D$ satisfies:
	\begin{equation}
		B \neq 0, BD \geq 0, BC>0,
	\label{eq:Riccati_assumptions}
	\end{equation}
	then it has a unique solution:
\begin{equation}
		\rho_t= \frac{(C+D \delta^+) - (C+D \delta^-) e^{-(\delta^+ - \delta^-)(T-t)}}{(-\delta^- + D B) + (\delta^+ - D B) e^{-(\delta^+ - \delta^-)(T-t)}}
	\label{eq:riccati_ut_sol_app}
\end{equation}
	where $\delta^\pm = -A \pm \sqrt{(A)^2 + B C}$.

>>>>

We study in the following the variation of $PoA$ by letting one of the coefficients tend to zero or to infinity. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right), & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1), & \qquad & 
		A^\eta &=& - b_1, \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}}, \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s)),& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2, & \qquad &
		C^\eta &=& q + \bar{q}, \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)), & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2, & \qquad & 
		D^\eta &=& q_T + \bar{q}_T .
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{C^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+D^u(\delta^+_u -\delta^-_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} )}{D^u B^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+ \delta^+_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} -\delta^-_u  },
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. Under assumption (\ref{eq:assumptions}), the above conditions on $B^u$, $C^u$, and $D^u$ are satisfied, and we have $\delta^-_u<0<\delta^+_u$, $u_t > 0$ for all $t\in[0,T)$, and $u_T \geq 0$. We have analogous expressions for $w_t$ and $\eta_t$, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +& D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )\\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)})& + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	% lower bound for (b_2 + b2 bar) u_t
	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}). Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$, for example $\epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$. Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
	$$ 
	so that
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}

@@

%	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	We first provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. Let $\epsilon_1 > 0$ satisfy $\epsilon_1 < \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$, there exists $\bar{b}_2^{*,u} := \bar{b}^{*,u}_2(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert \right\} \leq \epsilon_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$:
	\begin{IEEEeqnarray*}{rCl}
		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right)+ \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} - \delta_u^{-,\bar{b}_2} } \\
		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
		&\leq & \frac{\epsilon_1 + \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_u(\epsilon_1)
	\end{IEEEeqnarray*}
	Idem, we can also have a uniform bound for $w_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough. There exists $\bar{b}_2^{*,w} := \bar{b}_2^{*,w}(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,w}$ we have:
	\begin{equation*}
		\vert w_t^{\bar{b}_2} \vert \leq \frac{\epsilon_1 + D^w (2 c_{\delta_w^{\bar{b}_2\to \infty}} + 2 \epsilon_1)}{c_{\delta_w^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_w(\epsilon_1).		
	\end{equation*}
	Let $\bar{b}^{*,upper}_2 = \max\{ \bar{b}_2^{*,u}, \bar{b}_2^{*,w} \}$ and $M(\epsilon_1) = \max\{ M_u(\epsilon_1), M_v(\epsilon_1) \}$, then we have
	\begin{equation}
	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
	\end{equation}

@@

\subsection*{\textbf{Scalar Riccati Equation}} If the scalar Riccati equation 
	\begin{equation*}
		\dot{\rho}_t - B \rho_t^2 - 2A \rho_t  + C = 0 
	\end{equation*}
	with terminal condition $\rho_T = D$ satisfies:
	\begin{equation}
		B \neq 0, BD \geq 0, BC>0,
	\label{eq:Riccati_assumptions}
	\end{equation}
	then it has a unique solution:
\begin{equation}
		\rho_t= \frac{C(1-e^{-(\delta^+ - \delta^-)(T-t)})+D( \delta^+ -\delta^-e^{-(\delta^+ - \delta^-)(T-t)}) }{D B(1-e^{-(\delta^+ - \delta^-)(T-t)})+ \delta^+e^{-(\delta^+ - \delta^-)(T-t)}  -\delta^- }
	\label{eq:riccati_ut_sol_app}
\end{equation}
	where $\delta^\pm = -A \pm \sqrt{(A)^2 + B C}$.
